hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2025-03-03 inst/manuscript/paper.Rmd
checking data edits

We demonstrate the utility three functions: `summarize_temp()`, `plot_check_temp()`, and `check_continuous()`--using a simulated year-long data set (`year_sim`). This dataset contains temperature readings taken every thirty minutes, and its structure (dimentions and first six rows) is shown below.

@@

```{r}
#year_sim data dimensions
dim(year_sim)
#fist 6 rows of year_sim
head(year_sim)
```

@@

# now a year's worth of single-day data
dim(year_sim_summ)

>>>>

We demonstrate the utility three functions: `summarize_temp()`, `plot_check_temp()`, and `check_continuous()`--using a simulated year-long data set (`year_sim`). This dataset contains temperature readings taken every thirty minutes, and its structure (dimensions and first six rows) is shown below.

@@

```{r}
#year_sim data dimensions (rows x columns)
dim(year_sim)
#fist 6 rows of year_sim
head(year_sim)
```

@@

# now a year's worth of single-day data
# 365 days x two columns
dim(year_sim_summ)
